The \dealii Library, Version 9.2

### 2020-05-14 9.2/paper.tex

\usepackage{todonotes}

@@

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
    Martin Kronbichler,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
%     Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}), 
\end{itemize}
%
The major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item x \todo[inline]{Wolfgang to write about complex-valued output}
\item y \todo[inline]{Timo to write about problems and fixes for
  computations with more than $2^{32}$ unknowns}
\item z \todo[inline]{What else?}
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.

@@

@@

In addition, there are seven new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\todo[inline]{Zhuoran to write}
\item \texttt{step-50}
\todo[inline]{Timo/Conrad/... to write}
\item \texttt{step-58}
\todo[inline]{Wolfgang to write}  
\item \texttt{step-65}
\todo[inline]{Martin to write}  
\item \texttt{step-67}
\todo[inline]{Martin to write}  
\item \texttt{step-69}
\todo[inline]{Matthias/Ignacio to write}  
\item \texttt{step-70}
  \todo[inline]{Also need to update announce and announce-short if this
    makes it into the release.}
\end{itemize}

\todo[inline]{Do we have new code gallery programs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Support for large, fully distributed meshes}
\label{subsec:pfT}

\todo[inline]{Peter: Write something about p::f::T}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Better support for parallel $hp$-adaptive algorithms}
\label{subsec:hp}

\todo[inline]{Marc: Your section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Support for particle-based methods}
\label{subsec:particles}

\todo[inline]{Luca: Your section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Python interfaces}
\label{subsec:python}

\todo[inline]{What's new here? mention step-49 and step-53 versions written in python.}

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item
\end{itemize}

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
% updated 5/11/2020 MM
\todo[inline]{TODO: remove authors of paper}
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Daniel Arndt,
Wolfgang Bangerth,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Bruno Blais,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Thomas C. Clevenger,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Marc Fehling,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Timo Heister,
Luca Heltai,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Martin Kronbichler,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Matthias Maier,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Peter Munch,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Jean-Paul Pelteret,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Reza Rastak,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Ignacio Tomas,
Sara Tro,
Bruno Turcksin,
Ferdinand Vanmaele,
Zhuoran Wang,
David Wells,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.

>>>>

@@

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
%     Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

The major changes of this release are:
%
\begin{itemize}
\item
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}),
%   \item Dedicated support for symbolic algebra (see
%     Section~\ref{subsec:sd}),
%   \item Full support for $hp$~adaptivity in parallel computations (see
%     Section~\ref{subsec:hp}),
%   \item An interface to the HDF5 file format and libraries (see
%     Section~\ref{subsec:hdf5}),
%   \item Significantly extended GPU support (see Section~\ref{subsec:gpu}),
%   \item Parallel geometric multigrid (GMG) improvements (see
%     \cite{ClevengerHeisterKanschatKronbichler2019} and
%     Section~\ref{subsec:gmg}),
%   \item Four new tutorial programs (step-61, step-62, step-63, step-64),
%     as well as one new code gallery program (see
%     Section~\ref{subsec:steps}).
\end{itemize}
%
The major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item
% \item
%   The release contains a number of performance improvements and bug fixes for
%   the matrix-free framework. One notable improvement is the support for
%   renumbering of degrees of freedom within the cells for discontinuous
%   elements, avoiding some reshuffling operations across the SIMD lanes
%   with vectorization over several cells and faces, which is especially
%   useful on processors with AVX-512 vectorization (8 doubles), speeding up
%   operations by up to 10\%. Secondly, the strategy for the most efficient
%   tensor product evaluators according to the performance analysis of
%   \cite{KronbichlerKormann2019} in the context of more quadrature points than
%   shape functions has been revised for better performance.
%
% \item A new class \texttt{ParsedConvergenceTable} has been introduced
%   that greatly simplifies the construction of convergence tables,
%   reading the options for the generation of the table from a parameter
%   file, and providing methods that, combined with a parameter file,
%   allow one to generate convergence tables using one-liners in user
%   codes.
%
% \item
%   The \texttt{FE\_BernardiRaugel} class implements the non-standard
%   Bernardi-Raugel (BR) element that can be used to construct a stable
%   velocity-pressure pair for the Stokes equation \cite{BR85}. The BR
%   element is an enriched version of the $Q_1^d$ element with added bubble
%   functions on each edge (in 2d) or face (in 3d). It addresses the fact
%   that the $Q_1^d\times Q_0$ combination is not inf-sup stable (requiring a
%   larger velocity space), and that the $Q_2^d\times Q_0$ combination is
%   stable but converges with only first-order at the cost of the large
%   number of velocity unknowns. The BR space is thus intermediate between the
%   $Q_1^d$ and $Q_2^d$ spaces.
%
%   The element is currently only implemented for parallelogram meshes due to
%   difficulties associated with the mapping of shape functions: The shape
%   functions of the $Q_1^d$ part of the element need to be mapped as
%   scalars, as is common for the vector components of the $Q_1^d$ element;
%   on the other hand, the vector-valued edge bubble functions need to be
%   mapped using the Piola transform as is common for the Raviart-Thomas
%   element. \dealii{} does not currently have the ability to use different
%   mappings for individual shape functions, though this functionality is
%   planned for the next release.
%
% \item
%   The \texttt{FE\_NedelecSZ} class is a new implementation of the
%   N{\'e}d{\'e}lec element on quadrilaterals and hexahedra. It is based on
%   the work of Zaglmayr \cite{Zag06} and overcomes the sign conflict issues
%   present in traditional N{\'e}d{\'e}lec elements that arise from the edge
%   and face parameterizations used in the basis functions. Therefore, this
%   element should provide consistent results for general quadrilateral and
%   hexahedral elements for which the relative orientations of edges and
%   faces (as seen from all adjacent cells) are often difficult to establish.
%   The \texttt{FE\_NedelecSZ} element addresses the sign conflict problem by
%   assigning a globally defined orientation to local edges and faces. A
%   detailed overview of the implementation of the \texttt{FE\_NedelecSZ}
%   element in \dealii{} can be found in \cite{Kynch2017}.
%
% \item All of the elementary geometrical objects of the library (namely
%   \texttt{Point<dim>}, \texttt{Segment<dim>}, and
%   \texttt{BoundingBox<dim>}) have been augmented with the traits
%   needed to comply with \texttt{boost::geometry} concepts. A new
%   interface to \texttt{boost::geometry::index::rtree} has been added
%   that simplifies the construction of spatial indices based on points,
%   bounding boxes, or segments.
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{bla1}
\label{subsec:bla1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Improved large-scale performance}
\label{subsec:performance}

Large-scale simulations with 304,128 cores have revealed bottlenecks in release 
9.1 during initialization due to the usage of expensive collective operations 
like \texttt{MPI\_Allgather()} and \texttt{MPI\_\allowbreak Alltoall()}, e.g., during the 
pre-computation of the index ranges of all processes, which have been stored in  an array. 
This information is needed to set up 
the  \texttt{Utilities::MPI::Par\-ti\-ti\-oner} class. 
In release 9.2, we have removed such arrays and have replaced 
the \texttt{MPI\_Allgather}/\allowbreak\texttt{MPI\_\allowbreak Alltoall} 
function calls by consensus algorithms~\cite{hoefler2010scalable}, which can be 
found in the namespace \texttt{Utilities::\allowbreak MPI::\allowbreak ConsensusAlgorithms} (short: \texttt{CA}): now, only the locally relevant information about the index ranges is (re)computed when needed, using these algorithms. 
We provide two flavors of the consensus algorithm: the two-step 
approach \texttt{CA::PEX} and the \texttt{CA::NBX}, 
which uses only point-to-point communications and a single \texttt{MPI\_IBarrier()}.

%Consensus algorithms are algorithms dedicated to efficient dynamic-sparse 
%communication patterns. In this context, the term ``dynamic-sparse'' means 
%that by the time this function is called, the other processes do not know 
%yet that they have to answer requests and
%each process only has to communicate with a small subset of processes of the 
%MPI communicator. We provide two flavors of the consensus algorithm: the two-step 
%approach \texttt{ConsensusAlgorithms::PEX} and the \texttt{ConsensusAlgorithms::NBX}, 
%which uses only point-to-point communications and a single \texttt{MPI\_IBarrier()}. 
%The class \texttt{ConsensusAlgorithms::Selector} selects one of the two previous 
%algorithms, depending on the number of processes.

Users can apply the new algorithms for their own dynamic-sparse problems by 
providing a list of target 
processes and pack/unpack routines either by implementing the interface 
\texttt{CA::\allowbreak Process} or by providing \texttt{std::function} 
objects to \texttt{CA::AnonymousProcess}.

By replacing the collective communications during setup and removing the arrays 
that contain information for each process (enabled by the application of consensus 
algorithms and other modifications---a full list of modifications leading to this 
improvement can be found online), we were able to significantly improve the setup 
time for large-scale simulations and to solve a Poisson problem with multigrid 
with 12T unknowns. 
Figure~\ref{} compares the timings of a simulation (incl. setup) with the 
previous release 9.1 and with the current release 9.2. 
{\color{red}TODO[Peter/Martin] description of the results}

The new code has been also applied to solve problems with adaptively refined 
meshes with more than 4B unknowns. {\color{red}TODO[Timo]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A new fully distributed triangulation class}
\label{subsec:pft}

By release 9.1, all triangulation classes of \texttt{deal.II} have in common that the coarse grid is shared by 
all processes and the actual mesh used for computations is constructed by repeated 
refinement. However, this has its limitations in industrial applications where, often, the mesh comes 
from an external mesh generator in the form of a file that already contains millions 
or tens of millions of cells. For such configurations, applications might already 
run out of  main memory, while reading the complete mesh by each MPI process.

The new class \texttt{parallel::fullydistributed::Triangulation} targets this issue 
by distributing also the coarse grid. Such 
a triangulation can be created by providing to each process a \texttt{Triangulation\-De\-scrip\-tion::Description} struct, containing 
1) the relevant data to construct the local part of the coarse grid, 2) the 
translation of the local coarse-cell IDs to globally unique IDs, 3) the hierarchy 
of mesh refinements, and 4) the owner of the cells on the active mesh level as well 
as on the multigrid levels. Once the triangulation is set up with this struct, no adaptive
changes to the mesh are allowed at the moment.

%The \texttt{TriangulationDescription::Description} struct can be filled manually or 
%by the utility functions from the \texttt{TriangulationDescription::Utilities} 
%namespace. The function \texttt{create\_\allowbreak description\_\allowbreak 
%from\_ \allowbreak triangulation()} can convert a base triangulation (partitioned 
%serial \texttt{Tri\-angulation} and \texttt{parallel::distributed::Triangulation}) 
%to such a struct. The advantage of this approach is that all known utility 
%functions from the namespaces \texttt{GridIn} and \texttt{GridTools} can be used 
%on the base triangulations before converting them to the structs. Since this 
%function suffers from the same main memory problems as described above, we also 
%provide the function \texttt{create\_description\_from\_triangulation\_in\_groups()}, 
%which creates the structs only on the master process in a process group. These 
%structs are filled one by one and are sent to the relevant processes once they are 
%ready. A sensible process group size might contain all processes of one compute node.

The new fully distributed triangulation class works---in contrast to  
\texttt{parallel::distributed::\allowbreak Tri\-an\-gu\-la\-tion}---not only for 2D- and 3D- but also for 
1D-problems. It can be used in the context of geometric multigrid methods and 
supports periodic boundary conditions. Furthermore, hanging nodes are supported.

%We intend to extend the usability of the new triangulation class in regard of 
%different aspects, e.g., I/O. In addition, we would like to enable adaptive mesh 
%refinement, a feature of the other triangulation classes, which is very much 
%appreciated by many users. For repartitioning, we plan to use an oracle approach 
%known from \texttt{parallel::distributed::Triangulation}. Here, we would like to 
%rely on a user-provided partitioner, which might also be a graph partitioner.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advances of the SIMD capabilities and the matrix-free infrastructure}
\label{subsec:mf}

%\begin{itemize}
%\item ECL
%\item VectorizedArrayType
%\end{itemize}

The class \texttt{VectorizedArray<Number>} is a key ingredient for the high 
node-level performance of the matrix-free algorithms in deal.II~\cite{KronbichlerKormann2012, KronbichlerKormann2019}. It is a wrapper 
class around $n$ vector entries of type \texttt{Number} and delegates relevant 
function calls to appropriate Intrinsics instructions. Up to release 9.1, the 
vector length $n$ has been set at compile time of the library to the highest 
possible value supported by the given processor architecture.

The class \texttt{VectorizedArray} has been made more user-friendly by making 
it compatible with the STL algorithms found in the header \texttt{<algorithm>}. 
The length of the  vector can now be queried by  \texttt{VectorizedArray::size()} and its underlying number type by \texttt{VectorizedArray::value\_type}. 
Furthermore, the \texttt{VectorizedArray} class supports range-based iterations over its entries and, i.a., the following 
algorithms: \texttt{std::\allowbreak ad\-vance()}, \texttt{std::distance()}, and \texttt{std::max\_element()}.

This class has been also extended with the second optional template argument 
\texttt{VectorizedArray<Number, size>} with \texttt{size} being related to the 
vector length, i.e., the number of lanes to be used and the instruction set to be 
used. By default, the number is set to the highest value supported by the given 
hardware. A full list of supported 
vector lengths is presented in Table~\ref{tab:vectorizedarray}.

All matrix-free related classes (like \texttt{MatrixFree} and \texttt{FEEvaluation}) 
have been templated with the floating-point number type \texttt{Number} (e.g. \texttt{double} or \texttt{float}); the computations were performed implicitly 
on \texttt{VectorizedArray<Number>} structs with the highest 
instruction-set-architecture extension, with each lane responsible for a separate 
cell (vectoriziation over elements). In release 9.2, all matrix-free classes 
have been extended with a new optional template argument specifying the 
\texttt{VectorizedArrayType}. This allows users to select the vector length/ISA and, 
as a consequence, the number of cells to be processed at once directly in their applications: 
The deal.II-based 
library \texttt{hyper.deal}~\cite{munch2020hyperdeal}, which solves the 6D Vlasov--Poisson equation with high-order 
discontinuous Galerkin methods (with more than 1024 degrees of freedom per cell), works with \texttt{MatrixFree} objects of different SIMD-vector 
length in the same application and benefits---in terms of performance---by the possibility of decreasing the number of cells processed by a single SIMD instruction.

\begin{table}
\caption{Supported vector lengths of the class \texttt{VectorizedArray} and 
the corresponding instruction-set-architecture extensions. }\label{tab:vectorizedarray}
\centering
\begin{tabular}{ccc}
\toprule
\textbf{double} & \textbf{float} & \textbf{ISA}\\
\midrule
VectorizedArray<double, 1> & VectorizedArray<float, 1> & (auto-vectorization) \\
VectorizedArray<double, 2> & VectorizedArray<float, 4> & SSE2 \\ 
VectorizedArray<double, 4> & VectorizedArray<float, 8> & AVX/AVX2 \\ 
VectorizedArray<double, 8> & VectorizedArray<float, 16> & AVX-512 \\ 
\bottomrule
\end{tabular}

\caption{Comparison of relevant SIMD-related classes in deal.II and C++20.}\label{tab:simd}
\centering
\begin{tabular}{cc}
\toprule
\textbf{VectorizedArray (deal.II)} & \textbf{std::simd (C++20)} \\
\midrule
VectorizedArray<Number> & std::experimental::native\_simd<Number> \\
VectorizedArray<Number, size> & std::experimental::fixed\_size\_simd<Number, size> \\ \bottomrule
\end{tabular}
\end{table}

A side effect of introducing the new template argument \texttt{VectorizedArrayType} 
in the \texttt{MatrixFree} classes is that any data structures 
\texttt{VectorizedArrayType} can be processed if they support required 
functionalities like \texttt{size()} or \texttt{value\_type}. In this context, we 
would like to highlight that the new \texttt{C++20} feature \texttt{std::simd} 
can be processed by the matrix-free infrastructure with minor internal 
adjustment as an open pull request shows 
(see \url{https://github.com/dealii/dealii/pull/9994}).  
Table~\ref{tab:simd} gives a comparison of the deal.II-specific SIMD classes and 
the equivalent C++20 classes. 
%We welcome the standardization of the SIMD 
%parallelization paradigm in C++ and intend to replace step by step our own 
%wrapper class, which has been continuously developed over the last decade. We 
%would like to emphasize that the work invested in this class was not in vain, 
%since many performance-relevant utility functions implemented with \texttt{VectorizedArray} in mind (e.g., \texttt{vectorized\_load\_and\_transpose} 
%and \texttt{vectorized\_transpose\_and\_store}) will be still used, since they 
%have not become part of the standard.

%Further additions to the \texttt{MatrixFree} infrastructure consist of:
%\begin{itemize}
%\item a new variant of \texttt{MatrixFree::cell\_loop()}: It takes two
%\texttt{std::function} objects with ranges on the locally owned degrees of freedom, one
%with work to be scheduled before the cell operation first touches some
%unknowns and another with work to be executed after the cell operation last 
%touches them. The goal of
%these functions is to bring vector operations close to the time when the
%vector entries are accessed by the cell operation, which increases the cache
%hit rate of modern processors by improved temporal locality. 
%\item a new form of loop \texttt{MatrixFree::loop\_cell\_centric()}: This 
%kind of loop can be used in the context of discontinuous Galerkin methods, 
%where both cell and face integrals have to be evaluated. While in the case of 
%the traditional \texttt{loop}, cell and face integrals have been performed 
%independently, the new loop performs all cell and face integrals of a cell in 
%one go. This includes that each face integral has to be evaluated twice, but 
%entries have to be written into the solution vector only once with improved 
%data locality. Previous publications based on \texttt{deal.II} have shown the 
%relevance of the latter aspect for reaching higher performance. 
%\end{itemize}

In a next step, we intend to support that users could set 
\texttt{VectorizedArrayType} to \texttt{Number}, which would lead to the usage not 
of \texttt{VectorizedArray<Number, 1>} but of a specialized code-path exploiting 
vectorization within an element~\cite{KronbichlerKormann2019}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advances in GPU support}
\label{subsec:gpu}

\begin{itemize}
\item overlapping of computation and communication in the case of CUDA-aware MPI
\end{itemize}

@@

In addition, there are seven new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\item \texttt{step-50}
\item \texttt{step-58}
\item \texttt{step-65} presents \texttt{TransfiniteInterpolationManifold}, a
manifold class that can propagate curved boundary information into the
interior of a computational domain, and \texttt{MappingQCache}, which can sample 
the information of expensive manifolds in the points of a \texttt{MappingQ} and 
cache it for further use.
\item \texttt{step-67} presents an explicit time integrator for the
compressible Euler equations discretized with a high-order discontinuous
Galerkin scheme using the matrix-free infrastructure. Besides the use of
matrix-free evaluators for systems of equations and over-integration, it also
presents \texttt{MatrixFreeOperators::CellwiseInverseMassMatrix}, a fast implementation
of the action of the inverse mass matrix in the DG setting using tensor
products. Furthermore, this tutorial demonstrates the usage of new 
pre and post operations, which can be passed to \texttt{cell\_loop()}, to schedule operations on sections of vectors close 
to the matrix-vector product to increase data locality 
and discusses performance-related aspects.
\item \texttt{step-69}
\item \texttt{step-70}
\end{itemize}

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 15 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item The functions:
\begin{itemize}
\item \texttt{DoFHandler::loccaly\_owned\_dofs\_per\_processor()}
\item \texttt{DoFHandler::loccaly\_owned\_mg\_dofs\_per\_processor()}
\end{itemize} have been deprecated. As discussed in Subsection~\ref{subsec:performance}, deal.II does not store information for all processes on all processes processes, but only the local information or the locally-relevant information. Users are asked to construct the global information on their own, e.g. by calling \texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.
\item

% \item The \texttt{VectorView} class was removed. We recommend either copying the
%       vector subset into a \texttt{Vector} or using a \texttt{BlockVector}.
% \item The function \texttt{Subscriptor::subscribe()}, used through the
%   \texttt{SmartPointer} class, now requires a pointer to a
%       \texttt{std::atomic<bool>} that tracks whether or not the pointer to the
%       subscribed-to object is still valid.
% \item The \texttt{ConstraintMatrix} class gained a template parameter for the scalar
%       type and was been renamed \texttt{AffineConstraints}. Several methods that
%       take vectors or matrices as arguments,
%       such as \texttt{AffineConstraints::distribute\_local\_to\_global()},
%       now require that all matrix and vector arguments have matching number
%       types.
% \item Similarly, the functions \texttt{create\_mass\_matrix} and
%       \texttt{create\_boundary\_mass\_matrix} in the \texttt{MatrixCreator}
%       namespace no longer
%       support matrix and vector objects of different types.
\end{itemize}

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
% updated 5/11/2020 MM - TODO: remove authors of paper
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Daniel Arndt,
Wolfgang Bangerth,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Bruno Blais,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Thomas C. Clevenger,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Marc Fehling,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Timo Heister,
Luca Heltai,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Martin Kronbichler,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Matthias Maier,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Peter Munch,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Jean-Paul Pelteret,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Reza Rastak,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Ignacio Tomas,
Sara Tro,
Bruno Turcksin,
Ferdinand Vanmaele,
Zhuoran Wang,
David Wells,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.
